---
title: "Chapter 6 (8th Edition): 6.1, 6.3, 6.5, 6.6, 6.10, 6.11, 6.17, 6.22, 6.23, 6.25, 6.36, 6.37 "
author: "Jeremy Ling & Emmanuel Mejia"
date: "April 16, 2018"
output: pdf_document
---

##6.1

\textbf{An engineer is interested in the effects of cutting
speed (A), tool geometry (B), and cutting angle (C) on the life
(in hours) of a machine tool. Two levels of each factor are
chosen, and three replicates of a $2^3$ factorial design are run.
The results are as follows:}

\textbf{(a) Estimate the factor effects. Which effects appear to be
large?}

```{r}
# creating data table
factorA = rep(c("-","+","-","+","-","+","-","+"), times = 3)
factorB = rep(c("-","-","+","+","-","-","+","+"), times = 3)
factorC = rep(c("-","-","-","-","+","+","+","+"), times = 3)
Rep = rep(c("I", "II", "III"), each = 8)
yield = c(22,32,35,55,44,40,60,39,31,43,34,47,45,37,50,41,25,29,50,46,38,36,54,47)

cutting.speed.long = data.frame(factorA, factorB, factorC, Rep, yield)

# linear regression
cutting.speed.lm=lm(yield ~ coded(factorA) * coded(factorB) * coded(factorC), cutting.speed.long)
summary(cutting.speed.lm)

# interaction plot
with(cutting.speed.long, interaction.plot(factorA, factorC, yield))
```

\textbf{(b) Use the analysis of variance to confirm your conclusions
for part (a).}

```{r}
# ANOVA test
cutting.speed.aov=aov(yield ~ factorA * factorB * factorC, cutting.speed.long)
summary(cutting.speed.aov)
mse=summary(cutting.speed.aov)[[1]][8,3]
mse
```
The variables that we find statistically significant also match our results from estimating factor effects in part a.

\textbf{(c) Write down a regression model for predicting tool life
(in hours) based on the results of this experiment.}

$$y = \beta_0 + \beta_1 X_1 + \beta_2 + X_2 + \beta_3 + X_3 + \beta_{1,3} X_1 X_3$$


\textbf{(d) Analyze the residuals. Are there any obvious problems?}

```{r}
res=cutting.speed.long$yield-fitted(cutting.speed.lm)
library(car)
qqPlot(res)
plot(fitted(cutting.speed.lm), res) 
```

We take a look at our normality plot and can state that normality is good. We take a look at our residual plot and see no patterns, our model is good.

\textbf{(e) On the basis of an analysis of main effect and interaction
plots, what coded factor levels of A, B, and C
would you recommend using?}



##6.3

\textbf{Find the standard error of the factor effects and
approximate 95 percent confidence limits for the factor effects
in Problem 6.1. Do the results of this analysis agree with the
conclusions from the analysis of variance?}

##6.5

\textbf{A router is used to cut locating notches on a printed
circuit board. The vibration level at the surface of the board
as it is cut is considered to be a major source of dimensional
variation in the notches. Two factors are thought to influence vibration: bit size (A) and cutting speed (B). Two bit sizes (1/16
and 1/8 in.) and two speeds (40 and 90 rpm) are selected, and
four boards are cut at each set of conditions shown below.
The response variable is vibration measured as the resultant
vector of three accelerometers (x, y, and z) on each test circuit
board.}

\textbf{(a) Analyze the data from this experiment.}

```{r}
A <- rep(c("-","+","-","+"), times = 4)
B <- rep(c("-","-","+","+"), times = 4)
Rep <- rep(c("I","II","III","IV"), each = 4)
Vibes <- c(18.2, 27.2, 15.9, 41.0, 18.9, 24.0, 14.5, 43.9, 12.9, 22.4, 15.1, 36.3, 14.4, 22.5, 14.2, 39.9)
router.long <- data.frame(A, B, Rep, Vibes)
```


\textbf{(b) Construct a normal probability plot of the residuals,
and plot the residuals versus the predicted vibration
level. Interpret these plots.}

\textbf{(c) Draw the AB interaction plot. Interpret this plot. What
levels of bit size and speed would you recommend for
routine operation?}

##6.6

\textbf{Reconsider the experiment described in Problem 6.1.
Suppose that the experimenter only performed the eight trials
from replicate I. In addition, he ran four center points and
obtained the following response values: 36, 40, 43, 45.}

\textbf{(a) Estimate the factor effects. Which effects are large?}

\textbf{(b) Perform an analysis of variance, including a check for
pure quadratic curvature. What are your conclusions?}

\textbf{(c) Write down an appropriate model for predicting tool
life, based on the results of this experiment. Does this
model differ in any substantial way from the model in
Problem 6.1, part (c)?}

\textbf{(d) Analyze the residuals.}

\textbf{(e) What conclusions would you draw about the appropriate
operating conditions for this process?}

##6.10

\textbf{In Problem 6.9, the engineer was also interested in
potential fatigue differences resulting from the two types of bottles.
As a measure of the amount of effort required, he measured
the elevation of the heart rate (pulse) induced by the task. The
results follow. Analyze the data and draw conclusions. Analyze
the residuals and comment on the model's adequacy.}

##6.11

\textbf{Calculate approximate 95 percent confidence limits
for the factor effects in Problem 6.10. Do the results of this
analysis agree with the analysis of variance performed in
Problem 6.10?}

##6.17

\textbf{An experimenter has run a single replicate of a 24
design. The following effect estimates have been calculated:}

\textbf{(a) Construct a normal probability plot of these effects.}

\textbf{(b) Identify a tentative model, based on the plot of the
effects in part (a).}

##6.22

\textbf{Semiconductor manufacturing processes have long
and complex assembly flows, so matrix marks and automated
2d-matrix readers are used at several process steps throughout
factories. Unreadable matrix marks negatively affect factory
run rates because manual entry of part data is required before
manufacturing can resume. A $2^4$ factorial experiment was conducted
to develop a 2d-matrix laser mark on a metal cover that
protects a substrate-mounted die. The design factors are A $
laser power (9 and 13 W), B $ laser pulse frequency (4000 and
12,000 Hz), C $ matrix cell size (0.07 and 0.12 in.), and D $
writing speed (10 and 20 in./sec), and the response variable is
the unused error correction (UEC). This is a measure of the
unused portion of the redundant information embedded in the
2d-matrix. A UEC of 0 represents the lowest reading that still
results in a decodable matrix, while a value of 1 is the highest
reading. A DMX Verifier was used to measure UEC. The data
from this experiment are shown in Table P6.5.}

\textbf{(a) Analyze the data from this experiment. Which factors
significantly affect UEC?}

\textbf{(b) Analyze the residuals from this experiment. Are there
any indications of model inadequacy?}

##6.23

\textbf{Reconsider the experiment described in Problem 6.20.
Suppose that four center points are available and that the UEC
response at these four runs is 0.98, 0.95, 0.93, and 0.96, respectively.
Reanalyze the experiment incorporating a test for curvature
into the analysis. What conclusions can you draw? What
recommendations would you make to the experimenters?}

##6.25

\textbf{Consider the single replicate of the $2^4$ design in
Example 6.2. Suppose that we had arbitrarily decided to analyze
the data assuming that all three- and four-factor interactions
were negligible. Conduct this analysis and compare your
results with those obtained in the example. Do you think that
it is a good idea to arbitrarily assume interactions to be negligible
even if they are relatively high-order ones?}

##6.36

\textbf{Resistivity on a silicon wafer is influenced by several
factors. The results of a $2^4$ factorial experiment performed
during a critical processing step is shown in Table P6.10.}

##6.37

\textbf{Continuation of Problem 6.36. Suppose that the
experimenter had also run four center points along with the 16
runs in Problem 6.36. The resistivity measurements at the center
points are 8.15, 7.63, 8.95, and 6.48. Analyze the experiment
again incorporating the center points. What conclusions
can you draw now?}

